---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# poker777

<!-- badges: start -->
<!-- badges: end -->

The goal of poker777 is to to facilitate the simulation and analysis of poker games. Package can be used to create scoreboards, create leaderboards, determine a winner of a game between 2 players, calculate balance poker chips in a player's hands.

The `poker_winner` function determines the winner of a poker game based on the hands of two players. It evaluates the best hand for each player and compares them to determine the winner or if it's a tie.

The `poker_balance_chips` function is designed to simulate the balance of chips for a player participating in a poker game. It takes into account various parameters such as buy-in limits, minimum bet requirements, player buy-in amount, and the outcome of each round of betting.

The `poker_leaderboard` function generates a leaderboard based on the winners of each round, as well as the pot and bet amounts. It arranges player positions and displays the net amount won and the number of rounds won by each player.

The `create_scoreboard` function is used to generate a scoreboard vector for each round of a poker game. This vector consists of information about the winner, pot amount, and bet amount for each round.

## Installation

You can install the development version of poker777 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Advanced-R-Programming/assignment-3-package-completion-hbsjain")
```

## Example

This is a basic example which shows you how to input the cards in each player's hands and find who wins the round.

```{r winner-example}
library(poker777)
# Define hands for two players
hands <- list(c("2h", "2h", "2h", "2h", "3h"), c("4h", "4h", "4h", "4h", "5h"))

# Determine the winner
winner <- poker_winner(hands)

# Print the winner
print(winner)
```

This is a basic example which shows you how to input the buyin limits, minimum bets allowed in each round, amount player used to buyin, and how much they bet and how much they won in each round. The output will be the total amount won for all rounds.

```{r balance-chips-example}
library(poker777)
# Define parameters
buy_in_limits <- c(100, 500)
min_bet <- 10
player_buy_in <- 200
bet_n_win <- list(c(20, 50), c(30, 0), c(50, 100))

# Call the function
remaining_chips <- poker_balance_chips(buy_in_limits, min_bet, player_buy_in, bet_n_win)

# Print the result
print(remaining_chips)
```

This is a basic example which shows you how to generate a leaderboard using the scoreboard vector which displays the winner of tournament in descending order along with how many rounds they won and how much they won and how much they bet.

```{r leaderboard-example}
library(poker777)
# Create a scoreboard
pot_wins <- create_scoreboard(c(1, 2, 3), c(5000, 3000, 4000), c(200, 500, 300))

# Generate leaderboard
leaderboard <- poker_leaderboard(pot_wins)

# Print the leaderboard
print(leaderboard)
```

This is a basic example which shows you how to create a scoreboard vector which has information about which player wins which round and how much they won and bet for that round.

```{r scoreboard-example}
library(poker777)
# Create a scoreboard
scoreboard <- create_scoreboard(c(1, 2, 3), c(5000, 3000, 4000), c(200, 500, 300))

# Print the scoreboard
print(scoreboard)
```
